Bayesian inference of prehistoric population dynamics from multiple proxies: a case study from the North of the Swiss Alps

### 2022-05-30 manuscript/paper_submission.Rmd
removed (useless) md versions of the paper
post zenodo deposition update of the submission version

    keep_md: yes

@@

>>>>

@@

# Code availability
The computer code used to generate the Bayesian Population model is provided in full in the Supplementary Information, together with information about the program and version used. The R code and Data are available online at https://github.com/MartinHinz/bayesian.demographic.reconstruction.2022 and is archived at https://doi.org/10.5281/zenodo.6594498.
